Statement-level AST-based Clone Detection in Java using Resolved Symbols

### 2019-11-06 benevol/paper.tex
Stuff again

	public void concatTen(String x) {
|\highlightYellow|		x = x + 10; // concat string
|\highlightYellow|		Notifier.notifyChanged(x);
|\highlightYellow|		return x;
	}
}
\end{javacode}}
\end{parcolumns}
\caption{Example of a type 1 clone that is functionally different.}
\label{fig:type1}
\end{figure*}

Most clone detection tools~\cite{kamiya2002ccfinder, semura2017ccfindersw, roy2008nicad, svajlenko2016bigcloneeval, svajlenko2014evaluating} detect type 1 clones by textually comparing code fragments (except for whitespace and comments). Although textually equal, method, type and variable references can still refer to different declarations. In such cases, refactoring opportunities could be invalidated. This can make type 1 clones less suitable for refactoring purposes, as they require additional judgment regarding the refactorability of such a clone.

Figure~\ref{fig:type1} shows a type 1 clone with two clone classes. Defining an automatic way to refactor these clone classes is nearly impossible, as both cloned fragments describe different functional behavior. The first cloned fragment is a method that adds something to a \texttt{List}. However, the \texttt{List} objects to which something is added are different. Looking at the \texttt{import} statement above the class, one fragment uses the \texttt{java.util.List} and the other uses the \texttt{java.awt.List}. Both happen to have an \texttt{add} method, but apart from that their implementation is completely different.

@@

This shows that not all type 1 clones can easily be automatically refactored. In section \label{chap:type1rclones} we describe an alternative approach towards detecting type 1 clones, which results in only clones that can be refactored.

>>>>

	public void concatTen(String x) {
|\highlightYellow|		x = x + 10; // concat string
|\highlightYellow|		Notifier.notifyChanged(x);
|\highlightYellow|		return x;
	}
}
\end{javacode}}
\end{parcolumns}
\caption{Example of a clone that, although textually equal, is contextually different.}
\label{fig:type1}
\end{figure*}

Most clone detection tools~\cite{kamiya2002ccfinder, semura2017ccfindersw, roy2008nicad, svajlenko2016bigcloneeval, svajlenko2014evaluating} detect clones by textually comparing code fragments (except for whitespace and comments). Although textually equal, method, type and variable references can still refer to different declarations. In such cases, refactoring opportunities could be invalidated. This can make clones less suitable for refactoring purposes, as they require additional judgment regarding the refactorability of such a clone.

Figure~\ref{fig:type1} shows two clone classes. Merging these clone classes is very hard (and likely not desirable), as both cloned fragments describe different functional behavior. The first cloned fragment is a method that adds something to a \texttt{List}. However, the \texttt{List} objects to which something is added are different. Looking at the \texttt{import} statement above the class, one fragment uses the \texttt{java.util.List} and the other uses the \texttt{java.awt.List}. Both happen to have an \texttt{add} method, but apart from that their implementation is completely different.

@@

This shows that not all textually equal clones can easily be refactored.

\section{CloneRefactor}
We develop a tool named CloneRefactor\footnote{CloneRefactor is available on GitHub: \url{https://github.com/SimonBaars/CloneRefactor}} that detects clones that can (relatively) easily be refactored. This tool uses JavaParser~\cite{tomassetti2017javaparser} to
